---
title: "W10 - Test Mining"
author: "Karim Hammoud"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: textmate
    toc: true
    toc_float: true
---

### Overview

In Text Mining with R, Chapter 2 looks at Sentiment Analysis.  In this assignment, you should start by getting the primary example code from chapter 2 working in an R Markdown document.  You should provide a citation to this base code.  You’re then asked to extend the code in two ways:

•	Work with a different corpus of your choosing, and

•	Incorporate at least one additional sentiment lexicon (possibly from another R package that you’ve found through research).

You can find the [rpubs file here]("https://rpubs.com/karim7mod/684218")

Set the environment

```{r message=FALSE}
library(janeaustenr)
library(gutenbergr)
library(stringr)
library(tidytext)
library(textdata)
library(jsonlite)
library(tidyverse)
library(wordcloud)
library(reshape2)
```

```{r}
get_sentiments("afinn")
```

```{r}
get_sentiments("bing")
```

```{r}
get_sentiments("nrc")
```

## Jane Austen dataset
```{r}
tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)
```

Filter sentiments of Joy words in Emma's book and get the count
```{r}
nrc_joy <- get_sentiments("nrc") %>%
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```


Count the positive and negative words 
```{r echo = FALSE}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


# plot the sentiment scores
ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

### compating three sentiments dictionaries

```{r}
pride_prejudice <- tidy_books %>% 
 filter(book == "Pride & Prejudice")

pride_prejudice
```


```{r}
afinn <- pride_prejudice %>% 
 inner_join(get_sentiments("afinn")) %>% 
 group_by(index = linenumber %/% 80) %>% 
 summarise(sentiment = sum (value)) %>% 
 mutate(method = "AFINN")
```

```{r}
bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing et al."),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```
                                
To compare the sentiments we plot them 
```{r}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

It looks like the NRC has the least negative sentiments, and it estimates more positive sentiments for the book.

```{r}
bing_word_counts <- tidy_books %>% 
 inner_join(get_sentiments("bing")) %>% 
 count(word, sentiment, sort = TRUE) %>% 
 ungroup
bing_word_counts
```

Now we can compare the negative and positive sentiments by plotting them and show the top 10 for each positive and negative
```{r echo = FALSE}
bing_word_counts %>%
 group_by(sentiment) %>%
 top_n(10) %>%
 ungroup() %>%
 mutate(word = reorder(word, n)) %>%
 ggplot(aes(word, n, fill = sentiment)) +
 geom_col(show.legend = FALSE) +
 facet_wrap(~sentiment, scales = "free_y") +
 labs(y = "Contribution to sentiment",
      x = NULL) +
 coord_flip()
```

```{r}
custom_stop_words <- 
 bind_rows(tibble(word = c("miss"),
                  lexicon = c("custom")),
           stop_words)

custom_stop_words
```

We get the wordclouds
```{r}
tidy_books %>% 
 anti_join(stop_words) %>% 
 count(word) %>% 
 
 
 
 with(wordcloud(word, n, max.words = 100))
```

Now we we to reshape the negative and positive sentiments
```{r}
tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(
    colors = c("gray20", "gray80"),
    max.words = 100
  )
```

### New Corpus 

I will use `My Bondage and My Freedom` is an autobiographical slave narrative written by `Frederick Douglass` and published in 1855. Download data using `gutenbergr` package.

Reference: https://docsouth.unc.edu/neh/douglass55/douglass55.html

```{r}
count_Bondage <- gutenberg_download(202) 

count_Bondage
```

### Convert Data to Tidy

```{r echo = FALSE}
count_Bondage_Freedom <- count_Bondage[c(763:nrow(count_Bondage)),]

Bondage_Chapters <- count_Bondage_Freedom %>% 
  filter(text != "") %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("CHAPTER [\\dIVXLC]", ignore_case =  TRUE)))) 

Bondage_Chapters
```

### Analysis

The most frequent used words for positive sentiments and negative sentiments.

```{r echo = FALSE}
Bondage_Sentiment <- Bondage_Chapters %>%
  unnest_tokens(word, text) %>% inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

Bondage_Sentiment %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() +
  geom_text(aes(label = n, hjust = 1.0))
```

#### Chapter wise positive and negative words
Group by chapter to get the positive/negative sentiments words.

we need now the total positive and negative word count using `bing` lexion.

```{r echo = FALSE, fig.height=30, fig.width=15}
Bondage_Freedom_Sentiment <- Bondage_Chapters %>%
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("bing")) %>%
  count(chapter, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


# here we have the plot for each chapter of the book.
ggplot(Bondage_Freedom_Sentiment, aes(index, sentiment, fill = chapter)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~chapter, ncol = 2, scales = "free_x")
```


Now we will use ~ 80 lines of text, to see which chapter has more negative sentiments and we see the chapter 25 has the most.

```{r echo = FALSE}
Positive_Negative<- Bondage_Chapters %>% 
   unnest_tokens(word, text) %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber %/% 80, chapter)%>%
  summarise(sentiment = sum(value))

Positive_Negative%>%
  ggplot(aes(chapter, sentiment, fill=index)) +
  geom_col()
```


#### Wordcloud

We need to check the most common words in "My Bondage and My Freedom".

```{r echo = FALSE}
word_count <- Bondage_Chapters %>% unnest_tokens(word, text) %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% filter(word != "thomas" )

word_count %>% with(wordcloud(word, n, max.words = 100))
```

### Important words per chapter 

we need to check the important of the words in the book per chapter for each 25 one.

```{r fig.height= 30, fig.width=20, echo = FALSE}
book_words <- Bondage_Chapters %>%
  unnest_tokens(word, text) %>%
  count(chapter, word, sort = TRUE)

total_words <- book_words %>% 
  group_by(chapter) %>% 
  dplyr::summarize(total = sum(n))

book_words <- left_join(book_words, total_words)

book_words <- book_words %>%
  bind_tf_idf(word, chapter, n)

book_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))


#we plot the most important words

book_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(chapter) %>% 
  top_n(10) %>% 
  ungroup() %>% 
  ggplot(aes(word, tf_idf, fill = chapter)) +
  geom_col(aes(reorder(word, tf_idf),tf_idf),stat = "identity",show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~chapter, scales = "free") +
  coord_flip()
```
